---
title: "Peptide Analysis"
output: html_notebook
---

```{r}
install.packages("dplyr")
install.packages("tidyverse")
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

(click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r}
library("dplyr")
library(stringr)
library(tidyverse)
```



```{r}
# Nominal proteins w/ quantitites within the UPS standards
ups_ref <- read.csv("UPS Proteins.tsv",
                  header = TRUE) %>%
  select(ups_protein = X...UniProt.Accession.Number,
         ups1_amount = UPS1.Amount..fmol.,
         ups2_amount = UPS2.Amount..fmol.) %>%
  mutate(ups2_amount = gsub(",","",ups2_amount)) %>%
  mutate(ups1_amount = gsub(",","",ups1_amount))
row.names(ups_ref) = ups_ref$ups_protein

# Replicate 4 of the UPS1 data 
ups1_raw <- read.table("Data/UPS/UPS1/UPS1_04-Peptide_Shaker_on_data_24__Peptide_Report.tabular",
                   sep = "\t", comment.char="", header = TRUE) %>%
  select(ups1_protein = Protein.s.,
         Sequence,
         ups1_validated_psms = X.Validated.PSMs)

# Filters the dataset to keep only UPS proteins
ups1 <- filter(ups1_raw, grepl("ups", ups1_protein))

# Replicate 4 of the UPS2 data
ups2_raw <- read.table("Data/UPS/UPS2/UPS2_04-Peptide_Shaker_on_data_28__Peptide_Report.tabular",
                   sep = "\t", comment.char="", header = TRUE) %>%
  select(proteins = Protein.s.,
         Sequence,
         ups2_validated_psms = X.Validated.PSMs)

# Filters the dataset to keep only UPS proteins
ups2 <- filter(ups2_raw, grepl("ups", proteins)) %>%
  # Extracts the UPS protein's identifier
  extract(proteins,'ups_protein', regex = '.*([A-Z][0-9]+)ups.*', remove = FALSE) %>%
  # Matches the extracted ID to the UPS_ref df to obtain the nominal fmol amount
  mutate(amount = ups_ref[ups_protein,]$ups2_amount)

ups_proteins <- unique(ups2$ups_protein)
grouped_ups <- data.frame(protein = numeric(length(ups_proteins)), #This doesn't work with the character()
                          amount = numeric(length(ups_proteins)),
                          validated_psms = numeric(length(ups_proteins)))

for (i in seq_along(ups_proteins) ){
  grouped_ups$protein[i] <- ups_proteins[i]
  grouped_ups$amount[i] <- ups_ref[ups_proteins[i],]$ups2_amount
  grouped_ups$validated_psms[i] <- sum(ups2[which(ups2$ups_protein == ups_proteins[i]),]$ups2_validated_psms)
  #grouped_ups <- rbind(grouped_ups, data.frame(protein, "asdf","asdf"))
}
grouped_ups


#plot(as.numeric(ups2$amount), ups2$ups2_validated_psms, main="UPS2", 
 #    xlab="Nominal UPS2 amount (fmol)", ylab="Validated PSMs", pch=19)
```



Number of peptides found in the UPS datasets:
```{r}
paste('UPS peptides found in UPS1:', nrow(ups1))
paste('Total number of peptides found in UPS1:', nrow(ups1_raw))
```
```{r}
paste('UPS peptides found in UPS2:', nrow(ups2))
paste('Total number of peptides found in UPS2:', nrow(ups2_raw))
```


Extracts the fmol amount of UPS2 protein

```{r}
ups_ref[str_match('LALBA_HUMAN; P00709ups','.*(P[0-9]+)ups,*')[2],]$ups2_amount

```




